MINOS Handover Plots

### 2024-02-06 minos/validation/handovers.Rmd
Added a max_ncigs plot to handovers and small change in tobacco.py

@@

>>>>

### ncigs mean

@@

### ncigs Max

```{r}
raw.ncigs_max <- raw.dat %>%
  select(pidp, time, ncigs) %>%
  group_by(time) %>%
  summarise(max_ncigs = max(ncigs)) %>%
  mutate(source = 'final_US')

base.ncigs_max <- base.dat %>%
  dplyr::select(pidp, time, ncigs) %>%
  group_by(time) %>%
  summarise(max_ncigs = max(ncigs)) %>%
  mutate(source = 'baseline_output')

max_ncigs <- rbind(raw.ncigs_max, base.ncigs_max)

# Now plot
ggplot(data = max_ncigs, mapping = aes(x = time, y = max_ncigs, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Max ncigs', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')
```
